Probabilistic inference in dynamical systems

### 2025-05-27 nbs/concepts/inferenceindynamicalsystems/index.qmd
docs(inferenceindynamicalsystems): update imports from experimental models package
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

```{python}
# | label: transcription-splicing-degradation-simulation
# | code-fold: true
import diffrax
from pyrovelocity.models import solve_transcription_splicing_model
from pyrovelocity.models import solve_transcription_splicing_model_analytical
from pyrovelocity.logging import configure_logging
from jax import numpy as jnp

@@

import arviz as az
from pyrovelocity.models._deterministic_inference import (
    generate_posterior_inference_data,
    generate_prior_inference_data,
    generate_test_data_for_deterministic_model_inference,
    plot_sample_phase_portraits,
    plot_sample_trajectories,
    plot_sample_trajectories_with_percentiles,
    print_inference_data_structure,
)

>>>>

```{python}
# | label: transcription-splicing-degradation-simulation
# | code-fold: true
import diffrax
from pyrovelocity.models.experimental import ( 
    solve_transcription_splicing_model,
    solve_transcription_splicing_model_analytical,
)
from pyrovelocity.logging import configure_logging
from jax import numpy as jnp

@@

import arviz as az
from pyrovelocity.models.experimental import (
    generate_posterior_inference_data,
    generate_prior_inference_data,
    generate_test_data_for_deterministic_model_inference,
    plot_sample_phase_portraits,
    plot_sample_trajectories,
    plot_sample_trajectories_with_percentiles,
    print_inference_data_structure,
)
